---
title: "Hello R"
author: "Thomas Linden"
date: "Data 2401 - `r Sys.Date()`"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

datasaurus_dozen is a data frame with...

- 1846 rows
- 3 columns (variables):
  - dataset: indicates which dataset the data are from
  - x: x-values
  - y: y-values

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
r_dino = -0.0645

### Exercise 3

First let’s plot the data in the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between x and y in this dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
r_star = -0.0630

**Comparison**: r_dino is .0015 less than r_star.

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}


```

```{r}


```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
